Comparative RNA-Seq: Signal to Noise Documentation

### 2022-03-20 manuscript.Rmd
updates to readme

---
title: 'Comparative RNA-Seq: Signal to Noise Documentation'
author: "T.J Nicholson & P.P Gardner"
date: "March 2022"
output:
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: yes
editor_options:
  chunk_output_type: console
---

>>>>

---
title: 'Comparative RNA-Seq: Signal to Noise Documentation'
author: "T.J Nicholson & P.P Gardner"
date: "March 2022"
output:
  pdf_document: 
    highlight: "kate"
    toc: yes
    toc_depth: 4
  html_notebook:
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: yes
editor_options:
  chunk_output_type: console
---
